Market simulator

### 2020-11-11 analysis/05_market_simulator.Rmd
Testing update buttons
testing new way of importing data so we can use an apply button to change it with filInput

# Organization configuration
organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    organization_data <- read_csv(
      here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
    )
  } else {
    req(input$org_update)
    organization_data <- read_csv(input$org_update$datapath)
  }
})

@@

@@

### Imports

# actionButton(
#   "org_button",
#   label = "Update Organization Data"
# )

# Render the organization configurations as a table
renderTable({
  req(input$org_update)

  org_import = read_csv(input$org_update$datapath)
  org_import
})

>>>>

org_default <- read_csv(
    here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
  )

# Organization configuration
organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    organization_data <- org_default
  } else {
    eventReactive()
    req(input$org_update)
    organization_data <- read_csv(input$org_update$datapath)
  }
})

# organization_data <- reactive({
#   if (is.null(input$org_update$datapath)) {
#     organization_data <- org_default
#   } else {
#     req(input$org_update)
#     eventReactive(input$org_button, {
#       organization_data <- read_csv(input$org_update$datapath)
#     })
#   }
# })

# observeEvent(input$org_button, {
#   req(input$org_update)
#   organization_data$data <- read_csv(input$org_update$datapath)
# })

@@

Imports
--------------------------------------

actionButton(
  "org_button",
  label = "Update Organization Data"
)

# organization_data <- reactive({
#   eventReactive(input$org_button, {
#       req(input$org_update)
#       organization_data <- read_csv(input$org_update$datapath)
#   })
# })

# observeEvent(input$org_button, {
#     session$sendCustomMessage(type = 'testmessage',
#       message = 'Thank you for clicking')
#   })

# Render the organization configurations as a table
# renderTable({
#   req(input$org_update)
#   
#   org_import = read_csv(input$org_update$datapath)
#   org_import
# })

@@
